Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-05 doc/paper.Rmd
small changes

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = miss/85491*100, shape=factor(wv), colour = factor(match))) + 
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.")
```

>>>>

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = miss/85491*100, shape=factor(wv), colour = factor(match))) + 
  geom_smooth(method="lm", size=.5, se=FALSE) +
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Size of optimization window") +
  scale_colour_brewer("Match", palette="Set1") +
  scale_shape_discrete("Size of \nvalidation\nwindow")
